---
title: "Lab 3 Mireia"
author: "Mireia Valle"
date: "23/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      messages = FALSE, 
                      warning = FALSE)
library(tidyverse)
library(janitor)
library(here)
library(sf)
#install.packages("XML")
library(XML)
#install.packages("tmap")
library(tmap)
```

##Binary logistic regression: Penguins!

Read in the data: 

```{r}
gentoo <- read_csv("gentoo_lter.csv")
chinstrap <- read_csv("chinstrap_lter.csv")

# Use full_join() to merge them together (keeping everything)
penguins <- full_join(chinstrap, gentoo) %>% 
  clean_names() %>%
  mutate(sex = str_to_lower(sex)) %>% 
  filter(sex %in% c("male", "female"))
```

Now let's graph this: 

```{r}
ggplot(data=penguins, aes(x = sex, y = body_mass_g))+
  geom_jitter(
    aes(color = sex, 
        pch = sex)
  ) + 
  facet_wrap(~species)
```

Code Chinstrap penguins as (1) and Gentoo penguins as (0): 

```{r}

unique(penguins$species)# to get the species names on the dataset

penguin_bin <- penguins %>% 
  #we want to create a new column, we use mutate
  mutate(
    #the new column is named species and will be filled under a if statement
     sp_binary= case_when(
      species == "Chinstrap penguin (Pygoscelis antarctica)" ~ 1,
      species == "Gentoo penguin (Pygoscelis papua)" ~ 0#, 
      #if we would like to assign a value to a 3rd species we will write
      #T ~ 3
    )
  )
```

Now let's run our binay logistic regression: 

```{r}
penguin_bir <- glm(sp_binary ~ sex + body_mass_g, 
                   family = binomial, 
                   data = penguin_bin)

summary(penguin_bir)
```
#as body mass is getting bigger the probability for being penguin type 1 is decreasing (-0.01)

Let's make some predictions for penguins (classification...kinda):

1. What is the probability that a penguin is a Chinstrap penguin, if it weighs 4500 grams and is male?

To answer this question we create a new dataframe that has two columns with the varibles we used to create the model
```{r}
df_m4500 <- data.frame(sex = "male", body_mass_g = 4500)

#Find logg odds of this penguin being Chinstrap:
m4500_logodds <- predict(penguin_bir, newdata = df_m4500, type = "link")
m4500_logodds

m4500_prob <- predict(penguin_bir, newdata = df_m4500, type = "response")
m4500_prob
```
2. What is the probability that a penguin is Chinstrap, if it is recorder as female of 4000 g?

```{r}
df_f4000 <- data.frame(sex = "female", body_mass_g = 4000)

#Find logg odds of this penguin being Chinstrap:
f4000_logodds <- predict(penguin_bir, newdata = df_f4000, type = "link")
f4000_logodds

f4000_prob <- predict(penguin_bir, newdata = df_f4000, type = "response")
f4000_prob
```

Now let's make an entire data frame & use it to make then visualize logistic regression outcomes:

```{r}
penguins_mock <- data.frame(
  #we create 2*200 observation of body_mass equally spaced from 3000 to 6000, we used "length" but we can use "by" and define the increment we want
  body_mass_g = rep(seq(3000, 6000, length = 200), 2), 
  sex = c(rep("male", 200), rep("female", 200))
)
```

Now let's use those to make predictions for all of them: 

```{r}
full_predict <- predict(penguin_bir, newdata = penguins_mock, type = "response", se.fit = TRUE)

#Get those into a data frame, along with the mock data used to create them:

final_df <- data.frame(
  penguins_mock, 
  full_predict$fit, 
  full_predict$se.fit
)

colnames(final_df) <- c("penguin_mass", "sex", "probability", "se")
```

Now let's graph it!

```{r}
ggplot(data = final_df, aes(x= penguin_mass, y = probability)) +
  geom_line(aes(color = sex)) +
  geom_ribbon(aes(ymin = probability - se,
                  ymax = probability + se, 
                  fill = sex),
              alpha = 0.3)

```

##Now some spatial data with sf

Read in the spatial data using read_sf():
```{r}
cougars <- read_sf(dsn = here("cougar_connections"), layer = "ds1014") %>% clean_names()
```

```{r}
large_corridors <- cougars %>% 
  filter(area_ac > 20000) %>% 
  select(area_ac)

plot(large_corridors)
```

```{r}
cougar_sub <- cougars %>% 
  select(elev_mean)
```


in ggplot:

```{r}
ggplot(data = cougar_sub) +
  geom_sf(aes(fill = elev_mean),
          color = NA)
```

```{r}
tmap_mode("view")

tm_shape(cougar_sub) +
  tm_fill ("elev_mean")


```











